Preferential Return Behaviors in People's Daily Life: Evidence from semantic enriched geo-located Twitter data

### 2016-12-22 semantic_decomposition_of_twitter_user_locations/paper.tex
temp
try
Speed up

\begin{document}
% \title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
\title{A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations}
% \author~\thanks{yinjunjun@gmail.com]{Junjun Yin}
\author{Junjun Yin~\thanks{jyn@illinois.edu}}
\affil[1]{Department of Geography and Geographic Information Science}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
\renewcommand\Authands{ and }
\maketitle

@@

\section{Introduction}
With the advancements in mobile technology, the location information 
what is it?

>>>>

\begin{document}
% \title{A data synthesis approach for semantic decompositions of Twitter user locations: A case study of geo-located Twitter data in Chicago}
\title{A tale of two cities: A GIS based data synthesis approach to understanding semantic decompositions of Twitter user locations}
% \author~\thanks{yinjunjun@gmail.com]{Junjun Yin}
\author{Junjun Yin~\thanks{jyin@psu.edu}}
\affil[1]{Population Research Institute}
\affil[ ]{The Pennslyvania State University, State College, 16801, PA, USA}
\renewcommand\Authands{ and }
\maketitle

@@

\section{Introduction}

With the advancements in mobile technology, the location information 
what is it?

### 2016-12-22 sq_mobility/sq_mobility_twitter.tex
hurry up experiments
edits
Speed up

%\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
%\title{Sequential mobility patterns in people's daily life: Evidence from}
\title{Preferential Return Behaviors in People's Daily Life: Evidence from semantic enriched geo-located Twitter data}
\author[1,+]{Junjun  Yin}
\author[1,2,+]{Myeonghun Jeong}
\author[2,3,*]{Zhenhong Du}
\affil[1]{Department of Geography and Geographic Information Science}
\affil[2]{CyberGIS Center for Advanced Digitial and Spatial Studies}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
\affil[3]{Zhejiang University}
\affil[*]{duzhenhong.zju@gmail.com}
\affil[+]{these authors contributed equally to this work}

@@

\begin{abstract}
Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. Example Abstract. Abstract must be under 200 words and not include subheadings or citations. 
\end{abstract}

@@

>>>>

%\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
%\title{Sequential mobility patterns in people's daily life: Evidence from}
\title{Preferential Return Behaviors in People's Daily Life: Evidence from semantic enriched geo-located Twitter data}
\author[1,+]{Junjun  Yin}
% \author[1,2,+]{Myeonghun Jeong}
% \author[2,3,*]{Zhenhong Du}
\affil[1]{Population Research Institute}
\affil[ ]{The Pennslyvania State University, State College, PA, 16801, USA}
% \affil[2]{CyberGIS Center for Advanced Digitial and Spatial Studies}
% \affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}
% \affil[3]{Zhejiang University}
% \affil[*]{duzhenhong.zju@gmail.com}
\affil[+]{these authors contributed equally to this work}

@@

\begin{abstract}
Location Based Social Media provides 
\end{abstract}

@@

\section*{Author contributions statement}
J.Y. conceived the experiment(s),  J.Y. and M.J. conducted the experiment(s), J.Y., M.J. and D.Z. analysed the results.  All authors reviewed the manuscript.
